---
title: "Framingham Project -- Data Preliminaries"
author: "Adam Kuperavage"
date: "6/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries

```{r}
library(tidyverse)
```

## Load Data, Converted Integers into Doubles

```{r}
fram <- 
  read.csv("framingham.csv") %>% 
  mutate_if(is.integer, as.double) 

glimpse(fram)
```

## Skim Data

```{r}
fram %>% skimr::skim()
```

## Checked to see if non-smokers had missing values

```{r}
fram %>% 
  group_by(currentSmoker, cigsPerDay) %>% 
  summarise(n = n())
```

## Imputed Missing Values using Median, Skimmed Mutated Data

```{r}
fram_tbl <-   
  fram %>%  
  as_tibble() %>% 
  mutate(
    education = case_when(is.na(education) ~ median(education, na.rm = TRUE),
                          TRUE ~ education),
    cigsPerDay = case_when(is.na(cigsPerDay) ~ median(cigsPerDay, na.rm = TRUE), TRUE ~ cigsPerDay),
    BPMeds = case_when(is.na(BPMeds) ~ median(BPMeds, na.rm = TRUE),
                          TRUE ~ BPMeds),
    totChol = case_when(is.na(totChol) ~ median(totChol, na.rm = TRUE),
                        TRUE ~ totChol),
    BMI = case_when(is.na(BMI) ~ median(BMI, na.rm = TRUE),
                          TRUE ~ BMI),
    heartRate = case_when(is.na(heartRate) ~ median(heartRate, na.rm = TRUE),
                          TRUE ~ heartRate ),
    glucose = case_when(is.na(glucose) ~ median(glucose, na.rm = TRUE),
                        TRUE ~ glucose)
  )

fram_tbl %>% skimr::skim()
```


## Made the Values in the Code More Readable, Glimpsed at Readable Data
```{r}
fram_tbl <-   
  
  fram_tbl %>% 
  mutate(gender = case_when(male == 0 ~ "female",
                            male == 1 ~ "male"),
         education = as.character(education),
         currentSmoker = case_when(currentSmoker == 0 ~ "no",
                                   currentSmoker == 1 ~ "yes"),
         BPMeds = case_when(BPMeds == 0 ~ "no",
                            BPMeds == 1 ~ "yes"),
         prevalentStroke = case_when(prevalentStroke == 0 ~ "no",
                                     prevalentStroke == 1 ~ "yes"),
         prevalentHyp = case_when(prevalentHyp == 0 ~ "no",
                                  prevalentHyp == 1 ~ "yes"),
         diabetes = case_when(diabetes == 0 ~ "no",
                              diabetes == 1 ~ "yes"),
         TenYearCHD = case_when(TenYearCHD == 0 ~ "no",
                                TenYearCHD == 1 ~ "yes")) %>% 
  
  select(-male) %>% 
  mutate(TenYearCHD = as.factor(TenYearCHD))

fram_tbl %>% glimpse()
```

## Checked proportions of TenYearCHD

```{r}
fram_tbl %>% 
  count(TenYearCHD) %>% 
  mutate(prop = n/sum(n))
```

# 2. Data Splits

## Initial Split the Data, Checked Proportions

```{r}
set.seed(123)

splits <- initial_split(fram_tbl, strata = TenYearCHD)

fram_train <- training(splits)
fram_test <- testing(splits)
```

## Check Training Data

```{r}
fram_train %>% 
  count(TenYearCHD) %>% 
  mutate(prop = n/sum(n))
```

## Check Testing Data

```{r}
fram_test %>% 
  count(TenYearCHD) %>% 
  mutate(prop = n/sum(n))
```

## Split Validation Set

```{r}
set.seed(234)

val_set <- validation_split(fram_train,
                            strata = TenYearCHD,
                            prop = 0.80)
val_set
```

