---
title: "A Machine Learning Approach for Predicting the Ten-Year Risk of Coronary Heart Disease from the Framingham Heart Study Data"
#subtitle: 
author: "Anny Martinez-Velasquez, Adam Kuperavage"
institute: "Delaware State Univeristy, Dover, DE"
date: "8/6/2021"
output:
  xaringan::moon_reader:
    css: [default, rladies, rladies-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---



```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

# NOTE: Data_Prelim.Rmd and Log_Reg_Model.Rmd must be run first.

```

# Intro to Framingham Heart Study

- The Framingham Heart Study is an on-going long-term cardiovascular study originating in 1948. 

--

- It spans three generational cohorts plus additional cohorts for minorities and spouses.

--

- For our research, we decided to use a subset of the Framingham Heart Study consisting 4,239 individuals since it was accesible online at kaggle.com.

--

____

### The Big Question

__Can we build a machine learning model that can predict the probability of coronary heart disease (CHD) occurring within a ten-year time period?__

---

#Our variables

Our outcome/dependent variable is "TenYearCHD" which is what we are trying to predict. 

The rest were our independent variables that we will affect our predictions.

```{r}
fram_tbl %>% glimpse()
```

---

# Our Procedure
-  Used R programming language with supervised learning techniques that use labeled inputs with a trained model to reach desired outcomes when given new data. (Tidyverse, Tidymodels, Glmnet, and Shiny packages)

- Machine Learning is a subdivision of artificial intelligence that utilizes statistics and coding to make predictions.

- Machine Learning can be put into four steps: __extract features, split data, train the model, and evaluate findings.__

--

__First Steps__

 - Split the original data into a __training set and testing set.__
 
 - Subdivide the training set into __validation set__.

```{r}
set.seed(123)
splits <- initial_split(fram_tbl, strata = TenYearCHD)
fram_train <- training(splits)
fram_test <- testing(splits)
val_set <- validation_split(fram_train,
                            strata = TenYearCHD,
                            prop = 0.80)
```

---


# Model Comparison

We created multiple machine learning models such as __logistic regression, random forest, support vector machines, and stacked ensemble models__.

Each of these models are useful when dealing with binary classification problems. 

For our problem,the logistic regression model worked the best in terms of ROC AUC and accuracy.

Accuracy does not measure performance well when the dataset is unbalanced. 

--

| Models                  | ROC AUC   | Accuracy  |
|-------------------------|-----------|-----------|
| Logistic Regression     | 0.7246077 | 0.8528302 |
| Support Vector Machines | 0.7210703 | 0.8481132 |
| Random Forest           | 0.7056564 | 0.8471698 |
| Stacked Ensemble        | 0.7199718 | 0.8518868	|


---

# Logistic Regression Model

__Our Best Model:__
Logistic regression considers the relationship between a dependent variable and 15 independent variables and predicts the probability of whether a binary event will occur.

```{r}
lr_mod <- 
  logistic_reg(penalty = tune(), mixture = 1) %>% 
  set_engine("glmnet")
```

```{r}
lr_recipe <- 
  recipe(TenYearCHD ~ ., data = fram_train) %>% 
  step_dummy(all_nominal(), -all_outcomes()) %>% 
  step_zv(all_predictors()) %>% 
  step_normalize(all_predictors())
```

```{r}
set.seed(345)
lr_res <- 
  lr_workflow %>% 
  tune_grid(val_set,
            grid = lr_reg_grid,
            control = control_grid(save_pred = TRUE, save_workflow = TRUE),
            metrics = metric_set(roc_auc))
```
---

# Performance 

-  The last_lr_fit has an updated workflow complete with an adjusted penalty for the model. These are the metrics when the new workflow is introduced to new data. 

```{r}
last_lr_fit %>% 
  collect_metrics()
```

- The finished fitted model making predictions on ten-year CHD:

```{r}
predict(last_fitted_model, fram_test, type = "prob") %>%
  head(3)
```


---

# Conclusion

- The logistic regression model was the best model in terms of predictability performance when introduced new data. 

- Due to the simplicity of the logistic regression model, it makes interpreting easier which is beneficial in creating a potential aid in assessing CHD.

- The final logistic regression model was incorporated into a Shiny app and could serve as a potential aid to healthcare professionals. 

_____________________________________

### Future Endeavors

- Experimentation with more machine learning models that could yield better results

- Expand output on the app to include a more personalized explanation.

---

# Take a Look at Our Code

https://github.com/akuperavage/Framingham-Heart-Study-Model

__References__

Wickham et al., (2019). Welcome to the tidyverse. Journal of Open
  Source Software, 4(43), 1686, https://doi.org/10.21105/joss.01686
  
Kuhn et al., (2020). Tidymodels: a collection of packages for
  modeling and machine learning using tidyverse principles.
  https://www.tidymodels.org
  
Winston Chang, Joe Cheng, JJ Allaire, Carson Sievert, Barret
  Schloerke, Yihui Xie, Jeff Allen, Jonathan McPherson, Alan Dipert and
  Barbara Borges (2021). shiny: Web Application Framework for R. R
  package version 1.6.0. https://CRAN.R-project.org/package=shiny
  
Mahmood, S. S., Levy, D., Vasan, R. S., & Wang, T. J. (2014). The Framingham Heart    Study and the epidemiology of cardiovascular disease: a historical perspective.     Lancet (London, England), 383(9921), 999–1008.          https://doi.org/10.1016/S0140-6736(13)61752-3

__Acknowledgement__: This research is supported by NINDS grant #R25NS095371
