---
title: "Logistic Regression Model"
author: "Adam Kuperavage"
date: "6/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Load Libraries

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
library(glmnet)
```

# 2. Logistic Regression Model

## Logistic Regression Model Initiated
```{r}
lr_mod <- 
  logistic_reg(penalty = tune(), mixture = 1) %>% 
  set_engine("glmnet")

lr_mod
```

## Recipe for Preprocessing Data
```{r}
lr_recipe <- 
  recipe(TenYearCHD ~ ., data = fram_train) %>% 
  step_dummy(all_nominal(), -all_outcomes()) %>% 
  step_zv(all_predictors()) %>% 
  step_normalize(all_predictors())

lr_recipe %>% prep() %>% juice()
```

## Combined Model and Recipe to make Workflow

```{r}
lr_workflow <- 
  workflow() %>% 
  add_model(lr_mod) %>% 
  add_recipe(lr_recipe)
```

## Created Tuning Grid

```{r}
lr_reg_grid <- tibble(penalty = 10^seq(-4, -1, length.out = 30))

lr_reg_grid %>% head()
```

## Tune Model with Grid

```{r}
set.seed(345)

lr_res <- 
  lr_workflow %>% 
  tune_grid(val_set,
            grid = lr_reg_grid,
            control = control_grid(save_pred = TRUE, save_workflow = TRUE),
            metrics = metric_set(roc_auc))
lr_res
```

# Show Best Models

```{r}
lr_res %>% 
    show_best(metric = "roc_auc")
```



## Save Logistic Regression Models to a File

```{r}
#saveRDS(lr_res, "lr_res.rds")
```

# Show Best Model

```{r}
lr_best <- 
  lr_res %>% 
  select_best(metric = "roc_auc")

lr_best
```

# Last Model

```{r}
last_lr_mod <- 
  logistic_reg(penalty = lr_best$penalty, mixture = 1) %>% 
  set_engine("glmnet")
```


# Update Workflow

```{r}
last_lr_workflow <- 
  lr_workflow %>% 
  update_model(last_lr_mod)
```

# Last Fit

```{r}
last_lr_fit <- 
  last_lr_workflow %>% 
  last_fit(splits)

last_lr_fit
```


# Collect Metrics

```{r}
last_lr_fit %>% 
  collect_metrics()
```


# FINAL FITTED MODEL - USE THIS FOR PREDICTION

```{r}
last_fitted_model <- fit(last_lr_workflow, fram_train)
```


# Example

```{r}
predict(last_fitted_model, fram_test, type = "prob")
```


# Save to Project Folder

```{r}
saveRDS(last_fitted_model, "last_fitted_model.rds")
```


