---
title: "Rand_For_Model"
author: "Adam Kuperavage"
date: "6/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Load Libraries

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
library(ranger)
```


# 2. Random Forest Model 

## Random Forest Determine the Number of Cores

```{r}
cores <- parallel::detectCores()
cores
```

## Create Random Forest Model

```{r}
rf_mod <- 
  rand_forest(mtry = tune(), min_n = tune(), trees = 1000) %>% 
  set_engine("ranger", num.threads = cores) %>% 
  set_mode("classification")
```

## Random Forest recipe for Preprocessing Data

```{r}
rf_recipe <- 
  recipe(TenYearCHD ~ ., data = fram_train)
```

## Create Random Forest Workflow

```{r}
rf_workflow <- 
  workflow() %>% 
  add_model(rf_mod) %>% 
  add_recipe(rf_recipe)
```

## Confirm Tuning of Two Parameters

```{r}
rf_mod

rf_mod %>% 
  parameters()
```

## Tune along Grid Random Forest

```{r}
set.seed(345)

rf_res <- 
  rf_workflow %>% 
  tune_grid(val_set,
            grid = 25,
            control = control_grid(save_pred = TRUE, save_workflow = TRUE),
            metrics = metric_set(roc_auc))
rf_res
```

## Top 5 Best Random Forest Models out of 25

```{r}
rf_res %>% 
  show_best(metric = "roc_auc")
```

## Save Random Forest Models to a File

```{r}
#saveRDS(rf_res, "rf_res.rds")
```

# Show Best Model

```{r}
rf_best <- 
  rf_res %>% 
  select_best(metric = "roc_auc")

rf_best
```

# Last Model

```{r}
last_rf_mod <- 
  rand_forest(mtry = rf_best$mtry, min_n = rf_best$min_n, trees = 1000) %>% 
  set_engine("ranger", num.threads = cores) %>% 
  set_mode("classification")
```


# Update Workflow

```{r}
last_rf_workflow <- 
  rf_workflow %>% 
  update_model(last_rf_mod)
```

# Last Fit

```{r}
last_rf_fit <- 
  last_rf_workflow %>% 
  last_fit(splits)

last_rf_fit
```


# Collect Metrics

```{r}
last_rf_fit %>% 
  collect_metrics()
```


